Using reference models in variable selection \vspace{.1in}

### 2022-01-04 reviews/rebuttal.tex

% command declarations for reviewer points and our responses
\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~Point~\thepoint} } ---\ }
   {\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent 
	{\textbf{Reviewer~Point~\thepoint} } ---~#1\par }

\newenvironment{comment}
{\medskip \noindent \begin{sf}\textbf{Reviewer~comment}:\  }
	{\medskip \end{sf}}

@@

\paragraph{Associated Editor comment}
Please note the strong concerns of the reviewers. If you cannot implement a better projective prediction approach for complete variable selection problems, then at the very least, I would expect you to motivate why it's worth knowing about this approach; you show that it doesn't work very well.

\paragraph{Reply}
\fede{We have elaborated a better version of our paper following many of the reviewers' comments and suggestions. However, we believe that there has been a misunderstanding on the purpose of our work by Reviewer 1. The projective prediction approach for complete variable selection is not the aim of this work. The method has been included for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection. Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection. We do not exclude that better projective prediction method for complete selection can be designed in the future. \\
Reviewer 3 gave precious comments on how to clarify the real intentions of our work, which is the study of the effect of reference models when used to guide the selection process, regardless of the selection method. We followed the suggestions and we believe that the current version reduces the possibility of misunderstandings.}

%\todo
%\begin{description}
%    \item [Mans] Nothing
%\end{description}

% Let's start point-by-point with Reviewer 1
\reviewersection
\begin{comment}
The paper is well written and organized an the topic analyzed is very relevant and practice. However, in my view, the goals of the paper, described in the introduction section, have already been reached in the excellent paper of Pironen et al. (2020) and, in this sense, the contributions of the current paper is very marginal. The framework of Pironen et al. (2020) is more general (they consider exponential family models and generalized linear models) and provide some theoretical results that, as they said “... help us to understand when the reference model could be helpful for parameter learning in linear submodels” (section 8 of Piironen et al., 2020). The only innovation that I can appreciate in the current paper is the proposal of an algorithm to solve a complete variable selection problem that, unfortunately, does not work very well as the authors explicitly recognize: “The great performance of projpred in minimal subset selection is not carried out over for the complete variable selection with iterative projpred ..., and the methods specifically designed for the complete variable selection perform better” (page 12, lines 24-27), even though they observe a better selection to iterative lasso. In my view, this is due to that the algorithm is too simple (as the authors explicitly recognize in the conclusions) and that the projective prediction approach was not designed for the complete variable selection. You should modify this algorithm in such a way that a more exhaustive exploration of the space of models was carried out, perhaps using Bayesian variable selection procedures based on the use of Occam’s window or something similar.
\end{comment}

\begin{reply}
	\fede{Thank you for your comments. We believe that in the first version of the paper the purpouse of our work was not clear and subject to possible misunderstanding. Our contribution takes clear insipiration from the work of \citet{piironen2020projective}, but aims at a different goal. We studied what is the action of the reference model itself, disentangled from the specific variable selection algorithm.
	We made it clearer in Section 1, where we now write}

	\vspace{0.5cm}

	\textit{``The goal of our work is to study the impact of reference model approaches disentangling the benefit of the usage of a reference model from the specific selection algorithm. Specifically, we:
		\begin{itemize}
			\item disentangle the action of the reference model through a simple and intuitive way to combine any variable selection method with the reference model approach. This allows us to build up a comparison independent of the specific variable selection method;
			\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection and assessing the quality of the selection;
			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in variable selection.''
		\end{itemize}}

		\vspace{0.5cm}

		\fede{Moreover, the projective prediction approach for complete variable selection is not the aim of this work. The method has been included for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection. Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection. We do not exclude that better projective prediction method for complete selection can be designed in the future.}
\end{reply}

@@

% Point one description 
\begin{point}
My main concern with respect to the projective predictive approach is the robustness of the results to the reference model. Apparently, you can build very different references models to the same data set: have you study the sensitivity of the results with different reference models?. You use Bayesian models as reference models and, in these cases, the determination of prior distribution is not very clear. You can build hundreds and hundreds of prior distribution: for instance in (7) you can have use standard inverted gamma priors on $\tau^2$ and $\sigma^2$ by determining the parameters of the prior in order to the prior mixture gives reasonable results about the data using the prior mixture. How can you study the robustness of your results to this important aspect?
\end{point}

\begin{reply}
Thank you for your comments. We have added clarification at the end of Section 2.3 regarding the reference model, in particular we write that

\vspace{0.5cm}
\textit{
``Clearly, the reference model approach requires a sensible model. The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods. In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.''
}
\vspace{0.5cm}

So that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.

The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}. In this paper the point is not the Bayesian workflow, but to analyse given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.

The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues. As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
\end{reply}

@@

%\todo
%\begin{description}
%    \item[Mans] Clarified that we present first time how this problem should be approached in the Bayesian context.
%\end{description}

\begin{point}
Perhaps a solution to the previous problem would be to determine the reference model using frequentist MLE procedures that avoid the construction of prior distributions and use a single point prediction or, alternatively, to use the sampling distribution of MLE as a posterior distribution and take this “Bayesian” model as reference model. Do you have any experience in this line?
\end{point}

\begin{reply}
MLE is more unstable than Bayesian approach. The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors. We have added references that discuss merits of Bayesian approach compared to MLE \fede{not yet added!}. Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model.
\end{reply}

@@

No comments provided.

\reviewersection
%%%% REVIEWER 3

\begin{point}
Although main articles related to the use of the reference model approach in the model selection are mentioned, the motivation of the study in relation to the literature is missing in the Introduction. The given discussion of the existing literature supports the idea that the reference models have been used in Bayesian and non-Bayesian contexts. However, why do we need the proposed approach in the article is missing. Full motivation is given in Section 2. However, it needs to be briefly mentioned in the Introduction as well to motivate the reader to keep reading. In addition, instead of pointing to the references, please give a brief critique of them.
\end{point}

\begin{reply}
\fede{Thank you for the feedback. We renovated Section 1, improving the paper according to your suggestions. In particolar, we clarified what is the motivation of our work and, thus, what is the purpouse of the reference model approach used in our experiments. In the new version of the paper we write
}
\vspace{0.5cm}

\textit{``The goal of our work is to study the impact of reference model approaches disentangling the benefit of the usage of a reference model from the specific selection algorithm. Specifically, we:
	\begin{itemize}
		\item disentangle the action of the reference model through a simple and intuitive way to combine any variable selection method with the reference model approach. This allows us to build up a comparison independent of the specific variable selection method;
		\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection and assessing the quality of the selection;
		\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in variable selection.''
	\end{itemize}}

	\vspace{0.5cm}

\end{reply}

@@

\begin{point}
Please include the computational cost of compared approaches in Section 2.1. 
\end{point}

\begin{reply}
\fede{We touch the computational aspects in Section 2.2. The reference model approach has in general the additional cost of fitting a reference model. However, this is usually available when building up a model via robust workflows \citep{gelman2020bayesian}. Therefore, in these cases there is not additional cost. In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.}
\end{reply}

\begin{point}
Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.
\end{point}

\begin{reply}
\fede{We added a new Section 3.3 which summarises and elaborate the results of Section 3. In particular, we write:
}

\vspace{0.5cm}
\textit{
The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection with the reference model approach (see Figure 5 and Table 3). However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.
}
\vspace{0.5cm}
\end{reply}

### 2022-01-04 paper/ref_approach.tex
expanded answers including paper edits

\fede{Clearly, the reference model approach require a sensible model. The construcion of such a model should follow proper modelling workflow including model assessment and validation \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results.}

>>>>

\fede{Clearly, the reference model approach requires a sensible model. The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods. In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.}
